Testing traversability of protein tunnels with flexible ligands using motion planning

### 2017-06-14 paper.tex
Added \tylde command to typeset tilde

\newcommand{\red}[1]{\textcolor{red}{#1}}

@@

\begin{figure}
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\textwidth]{fig/accessibility}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/ligand-scale}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/throughput}
\end{tabular}
\caption{Tunnel properties mapped onto its surface.
Left: Accessibility --- green denotes parts that were accesed by the ligand easily while red denotes parts that were accessible only in about 10\% of computations.
Middle: Ligand scale --- the average scale of the ligand was \~50\% in orange parts, \~60\% in yellow parts, \~80\% in yellow to green parts and \~100\% in green parts.
Right: Throughput --- green denotes parts that are highly probable to be passed by the ligand while red denotes those that were hard to pass.}
\label{fig:properties}
\end{figure}

>>>>

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\tylde}{\raisebox{-0.85ex}{\textasciitilde}}

@@

\begin{figure}
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\textwidth]{fig/accessibility}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/ligand-scale}
\quad & \quad
\includegraphics[width=0.3\textwidth]{fig/throughput}
\end{tabular}
\caption{Tunnel properties mapped onto its surface.
Left: Accessibility --- green denotes parts that were accesed by the ligand easily while red denotes parts that were accessible only in \tylde 10\% of computations.
Middle: Ligand scale --- the average scale of the ligand was \tylde 50\% in orange parts, \tylde 60\% in yellow parts, \tylde 80\% in yellow to green parts and \tylde 100\% in green parts.
Right: Throughput --- green denotes parts that are highly probable to be passed by the ligand while red denotes those that were hard to pass.}
\label{fig:properties}
\end{figure}
